Results visualization across sites

### 2021-11-30 metanalysis_visualization/visualization.Rmd
ICD QC code updated adding upset for each disorder group and excel sheet with summary

# extract all codes that are available across all sites
codes_in_all_sites <- summary_codes[ complete.cases( summary_codes ), ]
codes_in_all_sites <- codes_in_all_sites[
  with(codes_in_all_sites, order(BCH, FRBDX, Lurie, UMICH, APHP, decreasing = TRUE)),
]
print( paste0("There are in total ", nrow( codes_in_all_sites), " codes in common across all sites"))

#### upSetR

BCH_concepts = mental_codes_qc_output_all[ mental_codes_qc_output_all$siteid == "BCH", "concept_code"]
FRBDX_concepts = mental_codes_qc_output_all[ mental_codes_qc_output_all$siteid == "FRBDX", "concept_code"]
Lurie_concepts = mental_codes_qc_output_all[ mental_codes_qc_output_all$siteid == "Lurie", "concept_code"]
UMICH_concepts = mental_codes_qc_output_all[ mental_codes_qc_output_all$siteid == "UMICH", "concept_code"]
APHP_concepts = mental_codes_qc_output_all[ mental_codes_qc_output_all$siteid == "APHP", "concept_code"]

concepts = list( 
          BCH = BCH_concepts$concept_code,
          FRBDX = FRBDX_concepts$concept_code, 
          Lurie = Lurie_concepts$concept_code, 
          UMICH = UMICH_concepts$concept_code, 
          APHP  = APHP_concepts$concept_code
          )

upset(fromList(concepts), order.by = "freq")

all_other_sites <- unique( c( FRBDX_concepts$concept_code, APHP_concepts$concept_code,
                              Lurie_concepts$concept_code, UMICH_concepts$concept_code ))
concepts_in_bch_not_in_other_sites <- BCH_concepts[! BCH_concepts$concept_code %in% all_other_sites, ]
codesToReview <- mental_codes_qc_output_all[ mental_codes_qc_output_all$concept_code %in% concepts_in_bch_not_in_other_sites$concept_code, ]

write.table( codesToReview, file="icdCodesOnlyInBCH.txt", col.names = TRUE, row.names = FALSE, sep = "\t", quote = FALSE )
write.table( codes_in_all_sites, file="icdCodesPresentInAllSites.txt", col.names = TRUE, row.names = FALSE, sep = "\t", quote = FALSE )
```

>>>>

## add a column with the sites combination 
getSitesWithEachCode <- function(row) {
  sites <- c( row['BCH'],  row['Lurie'], row['UMICH'], row['FRBDX'], row['APHP'])
  sites <- sites[!is.na( sites ) ]
  siteVal <- paste0( names( sites ), collapse = " - ")
  return( siteVal)
}
summary_codes <- summary_codes[, c("disorder_group", "description", "concept_code", 
                                   "BCH", "Lurie", "UMICH",  "FRBDX", "APHP") ]                        
summary_codes$sitesCombination <- apply(summary_codes, 1, FUN = getSitesWithEachCode)
summary_codes <- summary_codes[
  with(summary_codes, order(BCH, FRBDX, Lurie, UMICH, APHP, decreasing = TRUE)),
]
print( paste0("There are in total ", nrow( summary_codes[ summary_codes$sitesCombination == "BCH - Lurie - UMICH - FRBDX - APHP", ]), " codes in common across all sites"))

write.table( summary_codes, file="summary_codes.txt", col.names = TRUE, row.names = FALSE, sep = "\t", quote = FALSE )

#### upSetR 
upsetForDisorderGroup <- function( df, disorderGroup = "ALL"){
  if( disorderGroup != "ALL"){
     df <- df %>%
       filter( disorder_group == disorderGroup ) 
  }

  BCH_concepts = df[ df$siteid == "BCH", "concept_code"]
  FRBDX_concepts = df[ df$siteid == "FRBDX", "concept_code"]
  Lurie_concepts = df[ df$siteid == "Lurie", "concept_code"]
  UMICH_concepts = df[ df$siteid == "UMICH", "concept_code"]
  APHP_concepts = df[ df$siteid == "APHP", "concept_code"]

  concepts = list( 
          BCH = BCH_concepts$concept_code,
          FRBDX = FRBDX_concepts$concept_code, 
          Lurie = Lurie_concepts$concept_code, 
          UMICH = UMICH_concepts$concept_code, 
          APHP  = APHP_concepts$concept_code
          )
  output <- upset(fromList(concepts), order.by = "freq")
  return( output )
}

upsetForDisorderGroup( df = mental_codes_qc_output_all, disorderGroup = "ALL")
```

### UpSet R for each disorder group
```{r}
disorders <- unique( mental_codes_qc_output_all$disorder_group)
for( i in 1:length(disorders) ){
  print( disorders[i] )
  upsetForDisorderGroup( df = mental_codes_qc_output_all, disorderGroup = disorders[i])
}
```
